Structured and decorated cospans

### 2019-06-17 cospans.tex
more notation changes in Theorem 2.2

Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of underlying maps of cospans commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \otimes 0) \otimes M_2$};
\node (B) at (2.25,1) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_1 \otimes (0 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\rho \otimes 1$} (B)
(C) edge node[above]{$1 \otimes \lambda$} (B)
(A) edge node[above]{$a$} (C);
\end{tikzpicture}
\]
as well as the following triangle of corresponding decorations in the category $F(c_1+c_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})$};
\node (B) at (2.25,1) {$d_{M_1 \otimes M_2}$};
\node (C) at (4.5,0) {$F(1 \otimes \lambda)(d_{M_1 \otimes (0 \otimes M_2)}) $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\iota_{\rho \otimes 1}$} (B)
(C) edge node[right]{$\iota_{1 \otimes \lambda}$} (B)
(A) edge node[above]{$F(1 \otimes \lambda)(\iota_a)$} (C);
\end{tikzpicture}
\]
since $$F(\rho \otimes 1)(d_{(M_1 \otimes 0) \otimes M_2})=F((1 \otimes \lambda)a)(d_{(M_1 \otimes 0) \otimes M_2})$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes.

For a tensor product of objects $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}_1$, the source and target structure functors $S,T \colon F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
For two objects $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a_1+a_2$};
\node (A') at (0,-0.5) {$a_2+a_1$};
\node (B) at (2,0.5) {$c_1+c_2$};
\node (C) at (4,0.5) {$b_1+b_2$};
\node (C') at (4,-0.5) {$b_2+b_1$};
\node (D) at (2,-0.5) {$c_2+c_1$};
\node (E) at (5.5,0.5) {$d_{M_1 \otimes M_2} \in F(c_1+c_2)$};
\node (F) at (5.5,-0.5) {$d_{M_2 \otimes M_1} \in F(c_2+c_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$\beta_{a_1,a_2}$} (A')
(C) edge node[left]{$\beta_{b_1,b_2}$} (C')
(A') edge node [above]{$i_2+i_1$} (D)
(C') edge node [above]{$o_2+o_1$} (D)
(B) edge node [left] {$\beta_{c_1,c_2}$} (D);
\end{tikzpicture}
\]
$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{c_1,c_2})(d_{M_1 \otimes M_2}) \xrightarrow{\sim} d_{M_2 \otimes M_1}$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$. This braiding makes the following triangle of underlying cospans commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$M_1 \otimes M_2$};
\node (B) at (2.25,1) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_2 \otimes M_1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$\beta_{M_2,M_1}$} (B)
(A) edge node[above]{$\beta_{M_1,M_2}$} (C);
\end{tikzpicture}
\]
as well as the following diagram of corresponding decorations in the category $F(c_1+c_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$d_{M_1 \otimes M_2}$};
\node (B) at (2.25,1) {$d_{M_1 \otimes M_2} $};
\node (C) at (4.5,0) {$F(\beta_{c_2,c_1})(d_{M_2 \otimes M_1}) $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[right]{$\iota_{\beta_{M_2,M_1}}$} (B)
(A) edge node[above]{$F(\beta_{c_2,c_1})(\iota_{\beta_{M_1,M_2}})$} (C);
\end{tikzpicture}
\]
since $F(\beta_{c_2,c_1} \beta_{c_1,c_2}) (d_{M_1 \otimes M_2}) = d_{M_1 \otimes M_2}$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.

Now, given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
\node (D) at (1,-0.5) {$d_{M_1} \in F(b)$};
\node (F) at (4,0) {$b'$};
\node (G) at (5,0) {$a_3$};
\node (H) at (4,-0.5) {$d_{M_2} \in F(b')$};
\node (I) at (0,-1.5) {$a_1'$};
\node (J) at (1,-1.5) {$c$};
\node (K) at (2,-1.5) {$a_2'$};
\node (L) at (1,-2) {$d_{N_1} \in F(c)$};
\node (M) at (3,-1.5) {$a_2'$};
\node (N) at (4,-1.5) {$c'$};
\node (O) at (5,-1.5) {$a_3'$};
\node (P) at (4,-2) {$d_{N_2} \in F(c')$};

@@

\node (A) at (0,0) {$a_1+a_1'$};
\node (B) at (2.5,0) {$(b+c)+_{a_2+a_2'}(b'+c')$};
\node (C) at (5,0) {$a_3+a_3'$};
\node (D) at (2.5,-0.5) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};

@@

where the decoration $d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$ is given by:

@@

\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
\node (F) at (0,-5) {$F((b+c)+(b'+c'))$};
\node (G) at (0,-6) {$F((b+c)+_{a_2+a_2'}(b'+c'))$};

@@

(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
(E) edge node[left]{$\phi_{b+c,b'+c'}$} (F)
(F) edge node[left]{$F(j_{b+c,b'+c'})$} (G);

@@

\node (A) at (0,0) {$a_1+a_1'$};
\node (B) at (2.5,0) {$(b+_{a_2} c) + (b' +_{a_2'} c')$};
\node (C) at (5,0) {$a_3+a_3'$};
\node (D) at (2.5,-0.5) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};

@@

where the decoration $d_{((M_1 \odot M_2) \otimes (N_1 \odot N_2))} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$ is given by:

@@

\node (D) at (0,-3) {$(F(b) \times F(c)) \times (F(b') \times F(c'))$};
\node (E) at (0,-4) {$F(b+c) \times F(b'+c')$};
\node (F) at (0,-5) {$F(b+_{a_2}c) \times F(b'+_{a_2'}c')$};
\node (G) at (0,-6) {$F((b+_{a_2}c)+(b'+_{a_2'}c'))$};

@@

(C) edge node[left]{$(d_{M_1} \times d_{N_1}) \times (d_{M_2} \times d_{N_2})$} (D)
(D) edge node[left]{$\phi_{b,c} \times \phi_{b',c'}$} (E)
(E) edge node[left]{$F(j_{b,c}) \times F(j_{b',c'})$} (F)
(F) edge node[left]{$\phi_{b+_{a_2}c,b'+_{a_2'}c'}$} (G);

@@

\node (A) at (0,0.5) {$a_1+a_1'$};
\node (A') at (0,-0.5) {$a_1+a_1'$};
\node (B) at (2.5,0.5) {$(b+c)+_{a_2+a_2'}(b'+c')$};
\node (C) at (5,0.5) {$a_3+a_3'$};
\node (C') at (5,-0.5) {$a_3+a_3'$};
\node (D) at (2.5,-0.5) {$(b+_{a_2}c)+(b'+_{a_2'}c')$};
\node (E) at (2.5,1) {$d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)} \in F((b+c)+_{a_2+a_2'}(b'+c'))$};
\node (F) at (2.5,-1) {$d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)} \in F((b+_{a_2}c)+(b'+_{a_2'}c'))$};

@@

$$\iota_{\hat{\chi}} \colon F(\hat{\chi})(d_{(M_1 \otimes N_1) \odot (M_2 \otimes N_2)}) \to d_{(M_1 \odot M_2) \otimes (N_1 \odot N_2)}$$

>>>>

Similarly, if we denote the left and right unitors as $\lambda$ and $\rho$, respectively, then the following triangle of cospans and underlying maps of cospans commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \otimes 0) \otimes M_2$};
\node (B) at (2.25,1) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_1 \otimes (0 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\rho \otimes 1$} (B)
(C) edge node[above]{$1 \otimes \lambda$} (B)
(A) edge node[above]{$a$} (C);
\end{tikzpicture}
\]
as well as the following triangle of corresponding decorations in the category $F(m_1+m_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$F(\rho \otimes 1)((x_1+0)+x_2)$};
\node (B) at (2.25,1) {$x_1+x_2$};
\node (C) at (4.5,0) {$F(1 \otimes \lambda)(x_1+(0+x_2)) $};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\iota_{\rho \otimes 1}$} (B)
(C) edge node[right]{$\iota_{1 \otimes \lambda}$} (B)
(A) edge node[above]{$F(1 \otimes \lambda)(\iota_a)$} (C);
\end{tikzpicture}
\]
since $$F(\rho \otimes 1)((x_1+0)+x_2)=F((1 \otimes \lambda)a)((x_1+0)+x_2)$$ as the corresponding triangle in the symmetric monoidal category $(\mathsf{A},+,0)$ commutes and applying the pseudofunctor $F$ to this commutative triangle results in a commutative triangle in $\mathbf{Cat}$.

For a tensor product of objects $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}_1$, the source and target structure functors $S,T \colon F\mathbb{C}\textnormal{sp}_1 \to F\mathbb{C}\textnormal{sp}_0$ satisfy the following equations: $$S(M_1 \otimes M_2)=S(M_1) \otimes S(M_2)$$ $$T(M_1 \otimes M_2)=T(M_1) \otimes T(M_2).$$
For two objects $M_1$ and $M_2$ in $F\mathbb{C}\textnormal{sp}_1$, we have a braiding $\beta_{M_1,M_2} \colon M_1 \otimes M_2 \to M_2 \otimes M_1$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a_1+a_2$};
\node (A') at (0,-0.5) {$a_2+a_1$};
\node (B) at (2,0.5) {$m_1+m_2$};
\node (C) at (4,0.5) {$b_1+b_2$};
\node (C') at (4,-0.5) {$b_2+b_1$};
\node (D) at (2,-0.5) {$m_2+m_1$};
\node (E) at (5.5,0.5) {$x_1+x_2 \in F(m_1+m_2)$};
\node (F) at (5.5,-0.5) {$x_2+x_1 \in F(m_2+m_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$\beta_{a_1,a_2}$} (A')
(C) edge node[left]{$\beta_{b_1,b_2}$} (C')
(A') edge node [above]{$i_2+i_1$} (D)
(C') edge node [above]{$o_2+o_1$} (D)
(B) edge node [left] {$\beta_{m_1,m_2}$} (D);
\end{tikzpicture}
\]
$$\iota_{\beta_{M_1,M_2}} \colon F(\beta_{m_1,m_2})(x_1+x_2) \xrightarrow{\sim} x_2+x_1$$ where the vertical 1-morphisms are given by braidings in $(\mathsf{A},+,0)$. This braiding makes the following triangle of underlying cospans commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$M_1 \otimes M_2$};
\node (B) at (2.25,1) {$M_1 \otimes M_2$};
\node (C) at (4.5,0) {$M_2 \otimes M_1$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$\beta_{M_2,M_1}$} (B)
(A) edge node[above]{$\beta_{M_1,M_2}$} (C);
\end{tikzpicture}
\]
as well as the following diagram of corresponding decorations in the category $F(m_1+m_2)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$x_1+x_2$};
\node (B) at (2.25,1) {$x_1+x_2$};
\node (C) at (4.5,0) {$F(\beta_{m_2,m_1})(x_2+x_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[right]{$\iota_{\beta_{M_2,M_1}}$} (B)
(A) edge node[above]{$F(\beta_{m_2,m_1})(\iota_{\beta_{M_1,M_2}})$} (C);
\end{tikzpicture}
\]
since $F(\beta_{m_2,m_1} \beta_{m_1,m_2}) (x_1+x_2) = x_1+x_2$. Thus $F\mathbb{C}\textnormal{sp}_1$ is also symmetric monoidal.

Next we derive the globular isomorphisms required in the definition of a symmetric monoidal double category relating horizontal composition and the tensor product. Given four horizontal 1-cells $M_1, M_2, N_1$ and $N_2$ respectively by:
\node (I) at (0,-1.5) {$a'$};
\node (J) at (1,-1.5) {$n_1$};
\node (K) at (2,-1.5) {$b'$};
\node (L) at (1,-2) {$y_1 \in F(n_1)$};
\node (M) at (3,-1.5) {$b'$};
\node (N) at (4,-1.5) {$n_2$};
\node (O) at (5,-1.5) {$c'$};
\node (P) at (4,-2) {$y_2 \in F(n_2)$};

@@

\node (A) at (0,0) {$a+a'$};
\node (B) at (2.5,0) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
\node (C) at (5,0) {$c+c'$};
\node (D) at (2.5,-0.5) {$(x_1+y_1)\odot(x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};

@@

where the decoration $(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$ is given by:

@@

\node (D) at (0,-3) {$(F(m_1) \times F(n_1)) \times (F(m_2) \times F(n_2))$};
\node (E) at (0,-4) {$F(m_1+n_1) \times F(m_2+n_2)$};
\node (F) at (0,-5) {$F((m_1+n_1)+(m_2+n_2))$};
\node (G) at (0,-6) {$F((m_1+n_1)+_{b+b'}(m_2+n_2))$};

@@

(C) edge node[left]{$(x_1 \times y_1) \times (x_2 \times y_2)$} (D)
(D) edge node[left]{$\phi_{m_1,n_1} \times \phi_{m_2,n_2}$} (E)
(E) edge node[left]{$\phi_{m_1+n_1,m_2+n_2}$} (F)
(F) edge node[left]{$F(j_{m_1+n_1,m_2+n_2})$} (G);

@@

\node (A) at (0,0) {$a+a'$};
\node (B) at (2.5,0) {$(m_1+_{b} m_2) + (n_1 +_{b'} n_2)$};
\node (C) at (5,0) {$c+c'$};
\node (D) at (2.5,-0.5) {$(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};

@@

where the decoration $(x_1 \odot x_2) + (y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$ is given by:

@@

\node (D) at (0,-3) {$(F(m_1) \times F(m_2)) \times (F(n_1) \times F(n_2))$};
\node (E) at (0,-4) {$F(m_1+m_2) \times F(n_1+n_2)$};
\node (F) at (0,-5) {$F(m_1+_{b}m_2) \times F(n_1+_{b'}n_2)$};
\node (G) at (0,-6) {$F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};

@@

(C) edge node[left]{$(x_1 \times x_2) \times (y_1 \times y_2)$} (D)
(D) edge node[left]{$\phi_{m_1,m_2} \times \phi_{n_1,n_2}$} (E)
(E) edge node[left]{$F(j_{m_1,m_2}) \times F(j_{n_1,n_2})$} (F)
(F) edge node[left]{$\phi_{m_1+_{b}m_2,n_1+_{b'}n_2}$} (G);

@@

\node (A) at (0,0.5) {$a+a'$};
\node (A') at (0,-0.5) {$a+a'$};
\node (B) at (2.5,0.5) {$(m_1+n_1)+_{b+b'}(m_2+n_2)$};
\node (C) at (5,0.5) {$c+c'$};
\node (C') at (5,-0.5) {$c+c'$};
\node (D) at (2.5,-0.5) {$(m_1+_{b}m_2)+(n_1+_{b'}n_2)$};
\node (E) at (2.5,1) {$(x_1+y_1) \odot (x_2+y_2) \in F((m_1+n_1)+_{b+b'}(m_2+n_2))$};
\node (F) at (2.5,-1) {$(x_1 \odot x_2)+(y_1 \odot y_2) \in F((m_1+_{b}m_2)+(n_1+_{b'}n_2))$};

@@

$$\iota_{\hat{\chi}} \colon F(\hat{\chi})((x_1+y_1)\odot(x_2+y_2)) \to (x_1 \odot x_2)+(y_1 \odot y_2)$$
